Understanding Factors That Affects the Existence of Digital Innovation Hubs

### 2024-11-30 paper/paper.qmd
Model Completed

Despite the growing importance of innovation hubs in the global economy, the factors influencing the presence of Digital Innovation Hubs (DIH) in facilities remain underexplored and needed to be filled. This paper seeks to identify the key factors that influence whether a library in Toronto has a DIH, focusing on attributes such as area size, the number of public parking spots, the number of workstations in the library, and the number of years from the library was built.

@@

## Overview

@@

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

@@

Theeir descriptive statistics and graphs of their distribution is included in appendix (@sec-graph).

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

first_model <- readRDS(file = here::here("models/model.rds"))
```

@@

# Descriptive Statistics and Graphs of the Dataset {#sec-graph}

@@

data |> ggplot(aes(x = year)) +
  geom_histogram(col = "lightblue", fill = "lightblue", alpha = 0.8) +
  labs(x = "# of Workstations", y = "# of Libraries") +
  theme_minimal()
```

>>>>

Despite the growing importance of innovation hubs in the global economy, the factors influencing the presence of Digital Innovation Hubs (DIH) in facilities remain under-explored and needed to be filled. This paper seeks to identify the key factors that influence whether a library in Toronto has a DIH, focusing on attributes such as area size, the number of public parking spots, the number of workstations in the library, and the number of years from the library was built.

@@

@@

@@

Their descriptive statistics and graphs of their distribution is included in @sec-dsg.

The library dataset used in this study was collected through a combination of administrative records and self-reported surveys. While the dataset provides valuable insights, several factors need to be considered:

Reporting Variability: Libraries differ in how they track and report operational data, leading to potential inconsistencies. For instance, “workstations” might only include computers in some libraries, while others might also count other types of technological infrastructure.

Survey Limitations: The presence of a DIH was self-reported, which could result in over- or under-representation of actual DIHs. Some respondents might interpret “Digital Innovation Hub” differently based on their regional or institutional context.

Geographical Coverage: The dataset might not represent all regions equally. Libraries in rural areas may be underrepresented, impacting the generalization of the findings.

### Connection with Real-World

The dataset connects real-world phenomena to measurable entries. For example:

`area`: The size of a library, measured in square feet, reflects its physical capacity to host community activities, including DIHs. Size of library would affect the presence of DIHs.

`parking`: The number of parking spaces captures the the likelihood of a library being visited. If a library is more likely to be visited, it would have more facilities.

`workstations`: Number of workstations symbolize a library's technological infrastructure - computers and other digital tools that enable public access to the internet, software, and other resources. Libraries with more computers is likely to have DIHs.

`year`: Newer libraries are often designed to meet current technological needs, making them more suitable for DIHs.

`dih`: The presence of a DIH at a library provides a learning opportunity for the public.

@@

model <- readRDS(here::here("models/model.rds"))
```

In this analysis, a Bayesian logistic regression model was used to examine the relationship between the presence of a DIH in libraries and key library attributes. More details are included in @sec-md.

Our assumptions include that samples could represent every library in Toronto, observations should be independent with each other, and no perfect multicollinearity between predictor variables.

There are some limitations of our model. The model would be no longer valid if the actual underlying relationship between the predictor variables and the outcome variable is non-linear. Also, the predictor variables might not represent every aspect that would affect the presence of DIHs.

Additional predictor variables include position of the library (longitude and latitude). However, while the position of the library could affect the presence of DIHs indeed, the longitude and latitude are not associated with it linearly.

@@

Define $y_i$ as whether a library has a DIH (0 for no and 1 for yes) with probability $p_i$, so it follows a Bernoulli distribution. Then, the logistic link function of $p_i$ is a linear combination of the intercept - $\beta_0$, and the effects of the predictor variables - $\beta_1$, $\beta_2$, $\beta_3$, and $\beta_4$ times the predictor variables respectively.

\begin{align} 
y_i|p_i &\sim \mbox{Bern}(p_i) \\
\mbox{logit}(p_i) &= \beta_0 + \beta_1 \times \mbox{area}_i + \beta_2 \times \mbox{parking}_i + \beta_3 \times \mbox{workstations}_i + \beta_4 \times \mbox{year}_i \\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
\beta_3 &\sim \mbox{Normal}(0, 2.5) \\
\beta_4 &\sim \mbox{Normal}(0, 2.5)
\end{align}

Since we have no prior information about any variable, the prior of the intercept and coefficients was set to a normal distribution with $\mu=0$ and $\sigma=2.5$. We run the model in R [@r] using the `rstanarm` package [@rstanarm].

## Model justification

We propose the following hypotheses regarding how library attributes influence the likelihood of having DIHs.

`area`: We anticipate that larger libraries are more likely to host DIHs. Greater area reflects increased physical capacity, enabling libraries to allocate dedicated spaces for innovation and technology.

`parking`: The number of parking spaces is expected to positively correlate with the presence of a DIH. Parking facilities make libraries more accessible to the public, encouraging diverse patronage and increasing community engagement. Libraries with better accessibility might be more willing to improve its facilities and might receive greater funding and community support, promoting the establishment of advanced facilities like DIHs.

`workstations`: A strong positive relationship between the number of workstations and the presence of a DIH is expected. Workstations, representing technological infrastructure, are often central to the function of a DIH. Libraries with more workstations are likely equipped with the resources needed to support digital innovation and technological engagement.

`year`: We hypothesize a negative relationship between years since built and the likelihood of having a DIH. Older libraries might lack modern infrastructure and technological resources necessary for a DIH, whereas recently built or renovated libraries are more likely to own technological innovations aligned with the concept of a DIH.

@@

@@

# Descriptive Statistics and Graphs of the Dataset {#sec-dsg}

@@

data |> ggplot(aes(x = year)) +
  geom_histogram(col = "lightblue", fill = "lightblue", alpha = 0.8) +
  labs(x = "Age", y = "# of Libraries") +
  theme_minimal()
```

# Model Details {#sec-md}

```{r}
#| label: fig-posterior
#| fig-cap: Posterior Distribution for the Logistic Regression Model 
#| echo: false
#| warning: false
#| message: false

pp_check(model) +
  theme_minimal()
```

```{r}
#| echo: false
#| warning: false
#| message: false

pred <- fitted(model)
RMSE <- round(sqrt(mean((data$dih - pred) ^ 2)), 3)
```

The distribution of posterior is shown in @fig-posterior, which aligns with the actual data. From the graph, we can see that more libraries does not have a DIH. The $RMSE$ for our model is about `r RMSE`, which is a quite small value, meaning the model fits the data quite well.
